---
title: "Motility and Evenness"
author: "Christopher Bolte"
date: "February 20, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


**Part 1: Preparing Data**

Load the following packages:

```{r}
library(dplyr)
```


Obtain the original CSV from either the '.Rdata' file, or from the UCD Shared Drive (it's large, over 10 gb). After loading the .csv, run the following line of code.


```{r}
new_det <- select(det, DetectDate, Detection_GPS, TagID, Location, Species, Release_Location, Release_Date, Release_GPS, Release_rkm = Release_RKm, Detect_rkm = Detection_RKm, Length_Type, Tag_Type)

```

Make Initial Data.Frames by individual species

```{r}
g_sturg <- new_det[new_det$Species == 'Green_Sturgeon', ]
steelhead <- new_det[new_det$Species == 'Steelhead', ]
sevengill <- new_det[new_det$Species == 'Sevengill_Shark', ]
pikem <- new_det[new_det$Species == 'Sacramento_pikeminnow', ]
lmb <- new_det[new_det$Species == 'Largemouth_bass', ]
smb <- new_det[new_det$Species == 'Smallmouth_bass', ]
striped <- new_det[new_det$Species == 'Striped_bass', ]
white_cat <- new_det[new_det$Species == 'White_catfish', ]
w_sturg <- new_det[new_det$Species == 'White_Sturgeon', ]
chan_catfish <- new_det[new_det$Species == 'Channel_catfish', ]
spotted <- new_det[new_det$Species == 'Spotted_bass', ]
```

**Part 2: Load the Following 2 Functions**

Function: get_motility()

```{r}
get_motility <- function(df, low_rkm=0, high_rkm=550, species_name, str_startdate='2000-01-01 00:00:00', str_enddate='2100-01-01 00:00:00') {
  det <- df[df$Detect_rkm > low_rkm & df$Detect_rkm < high_rkm, ] #Takes detections only within specified rkms
  det <- df[df$DetectDate > str_startdate & df$DetectDate < str_enddate, ] #takes detections only within certain dates
  det$Detect_rkm <- as.numeric(det$Detect_rkm)
  det$Release_rkm <- as.numeric(det$Release_rkm)
  det <- det[is.na(det$Detect_rkm) == FALSE, ]
  det <- det[is.na(det$Release_rkm) == FALSE, ]
  all_tags <- c(unique(det$TagID))
  df_allmoves <- NULL
  count <- 1
  total_count <- length(all_tags)
  print(species_name)
  for (tag in all_tags) {
    print(paste(count, '/', total_count))
    ind_tag <- det[det$TagID == tag, ]
    ind_tag <- ind_tag[order(ind_tag$DetectDate), ]
    first_det <- min(ind_tag$DetectDate)
    last_det <- max(ind_tag$DetectDate)
    length <- ind_tag$Length[1]
    all_rows <- c(1:nrow(ind_tag))
    total_rkm <- abs(ind_tag$Release_rkm[1] - ind_tag$Detect_rkm[1])
    for (row in all_rows) {
      first_rkm <- ind_tag$Detect_rkm[row]
      second_rkm <- ind_tag$Detect_rkm[row + 1]
      if (row == nrow(ind_tag)) { #may need to add some subtleties to make sure that if the last detection is different from the second to last that this gets accounted for.
        species <- species_name
        df_allmoves <- rbind(df_allmoves, data.frame(tag, total_rkm, species, length, first_det, last_det))
        break
      }
      if (first_rkm != second_rkm) {
        diff_rkm <- abs(first_rkm - second_rkm)
        total_rkm <- total_rkm + diff_rkm
      }
    }
    count <- count + 1
  }
  return(df_allmoves)
}
```

Function: all_motility()

```{r}
all_motility <- function(l_detections, v_names, a_str_startdate='2000-01-01 00:00:00', a_str_enddate='2100-01-01 00:00:00') {
  total <- c(1:length(names))
  df_all_motility <- NULL
  if (length(l_detections) != length(v_names)) {
    print('The length of the two vectors or lists are not equivalent')
    break
  }
  for (t in total) {
    df <- data.frame(l_detections[t])
    species_name <- v_names[t]
    df_moves <- get_motility(df, species = species_name, str_startdate = a_str_startdate, str_enddate = a_str_enddate)
    df_all_motility <- rbind(df_all_motility, df_moves)
  }
  return(df_all_motility)
}
```


**Execute and Obtain Output**

Get the movements of ALL fish and then bind them into 1 large data frame with motility data for each fish. THIS WILL TAKE A LONG TIME!!!

```{r}
detections <- list(g_sturg, steelhead, pikem, lmb, smb, striped, white_cat, w_sturg, chan_catfish, spotted)
names <- c('green_sturgeon', 'steelhead', 'sacramento_pikeminnow', 'largemouth_bass', 'smallmouth_bass', 'striped_bass', 'white_catfish', 'white_sturgeon', 'channel_catfish', 'spotted_bass')


#FILL IN THE FOLLOWING STATEMENT WITH PREFERRED DATES TO OBTAIN MOTILITY FOR ALL SPECIES

#all_species_motility <- all_motility(l_detections = detections, v_names = names, a_str_startdate = , a_str_enddate = )
```


