---
title: "Eveness Data Preparation"
author: "Christopher Bolte"
date: "March 22, 2018"
output: html_document
---

**Part 1: Preparing Data**

Load the following packages:

```{r}
library(dplyr)
library(ggplot2)
```


Obtain the original CSV from either the '.Rdata' file, or from the UCD Shared Drive (it's large, over 10 gb). After loading the .csv, run the following line of code.


```{r}
new_det <- select(det, DetectDate, Detection_GPS, TagID, Location, Species, Release_Location, Release_Date, Release_GPS, Release_rkm = Release_RKm, Detect_rkm = Detection_RKm, Length_Type, Tag_Type)

```

Load the Following TWO Functions:

1. get_big_moves()   -- This function determines if there are any fish that have made a single movement over 100 rkm, then puts those fish's detections into a seperate data.frame.
```{r}

get_big_moves <- function(df_all_detections, taglist_colname = "TagID", rkm_threshold = 100) {
  det <- df_all_detections
  det <- det[is.na(det$Detect_rkm) == FALSE, ]
  det <- det[is.null(det$Detect_rkm) == FALSE, ]
  det <- det[det$Detect_rkm != 'NULL', ]
  det <- det[det$Detect_rkm != 'NA', ]
  det$Detect_rkm <- as.numeric(det$Detect_rkm)
  all_tags <- unique(det[[taglist_colname]])
  big_move_fish <- NULL
  count <- 1
  total_count <- length(all_tags)
  for (tag in all_tags) {
    print(paste(count, '/', total_count))
    print(tag)
    ind_tag <- det[det$TagID == tag, ]
    ind_tag <- ind_tag[order(ind_tag$DetectDate), ]
    if (nrow(ind_tag) > 0) {
      all_rows <- c(1:nrow(ind_tag))
      for (row in all_rows) {
        if (row == nrow(ind_tag)) { #end the current iteration of the for-loop because nothing fits the other criteria.
          print("There are no errant detections in the middle of this detection history above the specified threshold.")
          break
        }
        first_rkm <- ind_tag$Detect_rkm[row]
        second_rkm <- ind_tag$Detect_rkm[row + 1]
        diff_rkm <- abs(second_rkm - first_rkm)
        if (first_rkm != second_rkm & diff_rkm > rkm_threshold) {
          print("Movement greater than river kilometer threshold detected.")
          #Add detections to data.frame only with detections from these fish. In future data.frame, use unique() to get a list of TagIDs
          #to put into a river kilometer plots.
          big_move_fish <- rbind(big_move_fish, ind_tag)
          print(paste('TagID', tag, 'Added to new data.frame', sep = ' '))
          break
        }
      }
    }
    count <- count + 1
  }
  return(big_move_fish)
}
```


plot_rkm_time_vemco   --  plots the river kilomter vs time for detections in a target data.frame

```{r}
plot_rkm_time_vemco <- function(df, pdf_name, int_rkm = -100, str_start_datetime = "2000-01-01 00:00:00", str_end_datetime = "2050-01-01 00:00:00") {
  pdf(paste(pdf_name, ".pdf", sep = "" )) 
  df_edit <- df
  if (is.null(df_edit) == FALSE) {
  df_edit <- subset(df, Detect_rkm > int_rkm)
  df_edit <- subset(df_edit, DetectDate > str_start_datetime & DetectDate < str_end_datetime)
  all_tags <- unique(df$TagID)
  for (tag in all_tags) {
    df_id <-subset(df_edit, df_edit$TagID == tag)
    if (nrow(df_id) > 0) {
      df_id <- df_id[order(df_id$DetectDate), ]
      first_det <- min(df_id$DetectDate)
      last_det <- max(df_id$DetectDate)
      fish_move <- ggplot(df_id, aes(x=DetectDate, y=Detect_rkm, group = TagID)) +
        geom_point() + geom_line() +
        ggtitle(paste(tag, "from", first_det, "to", last_det)) +
        xlab("Time After Release") +
        ylab("River Kilometer")
      plot(fish_move)
      }
    }
  }
  dev.off()
}
```


Once those functions are loaded successfully, assign v_species to a vector of the species that you want to target, then run the following for loop. The function of this goes as follows.
1. Generates a data.frame with all of the detections from the specified species.
2. Dtermines which of those fish have allegedly made a movement over the specified number of river kilometers (default is 100)
3. Makes river kilometer plots of the fish that meet this criteria.


```{r}
v_species <- c('Green_Sturgeon', 'Steelhead', 'Sevengill_Shark', 'Sacramento_pikeminnow', 'Largemouth_bass', 'Smallmouth_bass', 
               'Striped_bass', 'White_catfish', 'White_Sturgeon', 'Channel_catfish', 'Spotted_bass')


for (species in v_species) {
  ind_species <- subset(new_det, Species == species)
  ind_species %>%
    get_big_moves %>%
      plot_rkm_time_vemco(paste('All', species, 'RKM plots with movement over 100 rkm'))
}
```

The final output from this should be river kilometer plots of individuals that have made a single movement of over 100 rkm. They will then need to be inspected to determine if the movements are acceptable.
Individuals that require adjustment can then have the following code run to remove those errant detections.

